---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
```

# targetRlynx

`targetRlynx` is an R package for parsing summary `.txt` files exported from TargetLynx, commonly used in LCMS workflows. It reads files and finds headers, extracts analyte blocks, and produces a clean data frame suitable for further analysis.

GitHub Repository: [bnilsson7/targetRlynx](https://github.com/bnilsson7/targetRlynx)

---

## Installation

```r
# Install from GitHub
remotes::install_github("bnilsson7/targetRlynx")
```

---

## Example Usage

```{r}
library(targetRlynx)

# Path to sample data
example_path <- system.file("extdata", "example_data_lynx_summary.txt", package = "targetRlynx")

# Parse single file
parsed <- processRlynx(example_path)
```

---

## Before & After Parsing

### Raw File Preview (First 10 lines)

```{r}
raw_lines <- readLines(example_path, warn = FALSE)
clean_lines <- iconv(raw_lines[1:10], from = "", to = "UTF-8", sub = "byte?")
cat(paste(clean_lines, collapse = "\n"))
```

### Parsed Output (First 10 rows)

```{r}
print(parsed[1:10, c(3,7:10)])
```

---

## Batch Parsing

```{r eval = FALSE}
# Parse all .txt files in a folder
results <- processRlynx("path/to/folder/")
```

---

## Functions

- `parse_one_file(path)`: Parses a single `.txt` file  
- `processRlynx(path)`: Parses one or many `.txt` files from a file or folder

Each row includes:
- Cleaned numeric columns
- Analyte label
- Source file name

---

## Citation

If you use this package in publications:

```
Nilsson, B. (2025). targetRlynx: Summary File Parser for TargetLynx. R package. https://github.com/bnilsson7/targetRlynx
```

---

## License

MIT © B. Nilsson
